Defending Byzantine Attacks in Ensemble Federated Learning: A Reputation-based Phishing Approach

### 2022-02-25 Manuscript_TIFS/manuscript_TIFS.tex
Byzantine client -> Byzantine attacker

\begin{abstract}
  Emerging as a promising distributed learning paradigm, federated learning (FL) has been widely adopted in many fields. Nonetheless, a big challenge for FL in real-world implementation is Byzantine attacks, where compromised clients can mislead or poison the training model by falsifying or manipulating the local model parameters. To solve this problem, in this paper, we present a reputation-based Byzantine robust-FL scheme (called FLPhish) for defending Byzantine attacks under the Ensemble Federated Learning architecture (called EFL). Specifically, we first develop a novel ensemble FL architecture, EFL, which allows FL compatible with different deep learning models in different clients. Second, we craft a phishing algorithm for the EFL architecture to identify possible Byzantine behaviors. Third, a Bayesian inference-based reputation mechanism is devised to measure each client's level of confidence and to further identify Byzantine clients. Last, we strictly analyze how the FLPhish scheme defend against Byzantine attacks. Extensive experiments under different settings demonstrate that the proposed FLPhish achieves great efficacy in defending Byzantine attacks in EFL. FLPhish is tested with different fractions of Byzantine clients and different degrees of distribution imbalance.
\end{abstract}

@@

\par Former researchers have offered certain Byzantine-robust techniques to deal with malicious Byzantine clients under the FL application settings \cite{ref_12_defense,ref_13_defense,ref_15_defense,ref_16_defense,ref_17_defense,ref_28_defense,ref_29_defense,ref_30_defense,ref_31_defense,ref_32_defense}. Byzantine-robust techniques try to construct a global model with high accuracy in the presence of a finite number of malicious clients. According to their different mechanisms, we divide Byzantine-robust approaches into two major types. The first (named Byzantine-Detection) is based on the development of a Byzantine-robust aggregation algorithm that distinguishes suspected clients from benign clients. The suspected clients' gradient updates are subsequently removed from the aggregation process by the server. For instance, in the DRACO scheme proposed by Chen \textit{et al.}, each node analyzes duplicate gradients that the parameter server uses to mitigate the effects of adversarial updates \cite{ref_13_defense}. Another Byzantine-robust technique (named Byzantine-Tolerance) seeks to ensure that the aggregation process is tolerant to poisoned updates from Byzantine clients without excluding Byzantine clients. For example, in Median \cite{ref_16_defense}, the FL server sorts the values of each parameter and picks the median value of each parameter as the value to be utilized in global model updates. In this study, we provide a unique reputation-based phishing method (named FLPhish) to protect against Byzantine attacks in EFL. Our contributions are three-fold:
\begin{itemize}
  \item We design a new FL architecture, Ensemble Federated Learning (called EFL), which utilizes an unlabeled dataset to replace the gradient updates in typical FL. This architecture is more compatible with different deep learning models on different clients.
  \item We craft a `phishing' method based on EFL to detect Byzantine attacks. The `phishing' method employs an labeled dataset to detect the potential Byzantine clients in the EFL architecture, which preserves the security of the EFL.
  \item We present a Bayesian inference-based reputation mechanism to promote FLPhish's aggregation. The reputation mechanism gives each client a reputation to measure its confidence value and identifies the clients with low reputation values as Byzantine clients, which helps FLPhish identify the Byzantine clients with higher accuracy.
\end{itemize}

\section{Related Work}
In this section, we discuss about the related research work about the proposed Byzantine defense methods in FL and the proposed reputation mechanism in cybersecurity research.
\subsection{Byzantine Defense Methods in Federated Learning}
Byzantine-robust schemes are very important for FL to enhance its security as Byzantine attacks can cause great damages to the FL system. Recent years have witnessed the increasing interest in the research of Byzantine-robust schemes in the context of FL. Most of the current Byzantine-robust FL methods tend to make a more robust aggregation rule which aims to tolerate the presence of Byzantine clients. 
For example, in 2017, Chen \textit{et al.} developed an approach called Krum, which selects one client's update as a global model based on a square-distance score in each iteration \cite{ref_12_defense}.
In the same year, Blanchard \textit{et al}. proposed two Byzantine-tolerant FL aggregation rules called Trimmed mean and Median \cite{ref_16_defense}. Trimmed Mean considers each parameter of the model update individually. Trimmed Mean sorts the parameter of the model updates collected, and cuts off the largest ones and the smallest ones. Median sorts the values of each parameter of all local model updates as well. Besides it considers the median value of each parameter as the value of the parameter in the global model update. 
In 2018, Chen \textit{et al.} designed an approach called DRACO to evaluate redundant gradients that are used by the parameter server to eliminate the effects of adversarial updates. 
In 2019, Xie \textit{et al.} proposed Zeno, which uses a ranking-based preference mechanism \cite{ref_15_defense}. The server computes a score for each client by using the stochastic zero-order oracle. Then Zeno presents a ranking list of clients based on the estimated descent of the loss function and the magnitudes. At last, Zeno computes the global model update by aggregating the clients with the highest scores. 
In 2020, SLSGD developed by Xie \textit{et al.} also uses trimmed mean as the robust aggregation rules for Byzantine-robust FL \cite{ref_14_defense}. 
In the same year, Cao \textit{et al.} proposed a Byzantine-tolerant scheme: FLTrust to introduce the use of trust \cite{ref_17_defense}. In each iteration, the server calculates a trust score for each client at first and lowers the trust score if the client's local model update's direction deviates more from the direction of the global model update. The client with a trust score lower than the threshold is considered a malicious client.
In 2021, a privacy-enhanced FL (PEFL) framework is presented by Liu \textit{et al.}  \cite{ref_45_defense}. PEFL takes advantage of homomorphic encryption to protect the privacy of the clients. Furthermore, a channel using the effective gradient data extraction is provided for the server to punish poisoners.

@@

\par \textit{1) Denial-of-Service Byzantine Attack:} In denial-of-service attacks, the Byzantine attackers intend to disturb the global model, thus making it produce wrong predictions of the normal dataset \cite{ref_04_model,ref_06_model,ref_07_data,yang2017generative,sun2018data}. The label flipping attack in the current system model can be used by a malicious Byzantine client $b_i$ to launch Byzantine attacks against the global model. Label flipping attacks require $b_i$ to change the labels of training data while ensuring that the data's features remain unchanged \cite{ref_18_label_flipping}. The local model of the Byzantine client, $b_i$ is trained with incorrect labels, resulting in a `poisoned' model with low accuracy. Then Byzantine client $b_{i}$ dispatches the false model gradient updates to the central server. Therefore, the false model gradient updates cause the central server to learn the false knowledge from clients. The server $s$'s aggregation process is performed on FedAvg, which takes each client $c_{i}$'s dataset $d_{i}$'s size as the aggregation weight for $c_{i}$. This means that a client $c_{i}$ with a larger size of $d_{i}$ gets a larger aggregation weight. Meanwhile, FedAvg takes the size of $d_{i}$ declared by $c_{i}$ as $d_{i}$'s real size, which means $b_{i}$ can declare a fake size value larger than $d_{i}$'s real size value to increase the impact of the attack. If the weight of the malicious clients reaches a threshold, the central server is misguided to produce false predictions. 

@@

\par \textit{1)} The typical FL design has several flaws, including incompatibility with various deep learning models in different clients and significant communication costs. As a result, we created EFL, a novel FL architecture inspired by the idea of ensemble learning. It lowers the cost of communication overhead and expands our ability to defend against Byzantine attacks in FL.
\par \textit{2)} The proposed EFL architecture currently needs a robust Byzantine attack protection mechanism. We urgently seek an efficient solution to deal with malicious Byzantine clients in FL because they cannot be trusted. In our proposed EFL architecture, we describe a phishing-based approach to guard against Byzantine attacks.
\par \textit{3)} As the performance of each client remains not stable in each iteration, it is important for our scheme to accurately measure each client's level of confidence in the long term. Therefore, we further propose an effective Bayesian inference-based reputation scheme based on our phishing-based model to spot Byzantine attacks compromised by malicious users.

@@

\begin{algorithm}[t]
  \caption{Phishing Mechanism} 
  \hspace*{0.02in} {\bf Input:} 
  each FL client $c_i$, $i=1,2,3,...,u$ with its local dataset $d_i$, $i=1,2,3,...,u$; an FL central server $s$ with the unlabeled dataset $D$ and labeled dataset $B$ preserved by itself; the number of FL training iterations $T$; the size of the unlabeled batch $n$ used in each training iteration; the size of the labeled batch $m$ used in each training iteration.\\
  \hspace*{0.02in} {\bf Output:} 
  output result
  \begin{algorithmic}[1]
    \State $\mathbf{m_i}$ $\gets$ each client $c_i$ train a local model using its local dataset $d_i$.
    \For{\textit{t=1,2,3,..,,T}}
      \State $s$ selects $D_t$ (containing $n$ samples) from $D$ and $B_t$ (containing $m$ samples) from $B$.
      \For{\textit{i=1,2,3,...,u}}
        \State $s$ sends $D_t$ and $B_t$ to $c_i$.
        \State $c_i$ makes predictions $\mathbf{k_i^t}$ of the $D_t$ and $B_t$.
        \State $c_i$ sends $\mathbf{k_i^t}$ to $s$.
        \State $s$ calculates the accuracy $a_i^t$ of the predictions of $B_t$ made by $c_i$ in $t$th procedure.
        \If{$a_i^t > r_q$}
          \State $q_i = 1$.
          \For{\textit{j=i,i+1,i+2,...,u-1}}
            \State $(d,c,\mathbf{k^t},q,a^t)_j \gets (d,c,\mathbf{k^t},q,a^t)_{j-1}$.
          \EndFor
        \EndIf
      \EndFor
      \State $\mathbf{K_t}$ = $KnowledgeEnsemble(\mathbf{k_1^t},\mathbf{k_2^t},\mathbf{k_3^t},...,\mathbf{k_u^t})$.
      \State $\mathbf{M}$ = $ModelUpdate(\mathbf{K_t}, D_t, \mathbf{M})$.
    \EndFor
    \State\Return $\mathbf{M}$
  \end{algorithmic}
  \end{algorithm}
Unlike benign clients, the malicious clients return the incorrect prediction to the central server $s$ to disturb the aggregation process.
\par Step-4: \ul{\textit{Byzantine Identifying}} After accepting the predictions $\mathbf{k_i^t}$ from each client $c_i$, $s$ needs to identify the Byzantine attackers among all the clients. The predictions of the \textit{`bait'} (the labeled dataset $B_t$) are extracted apart from $D_t$ from $\mathbf{k_i^t}$. Next, $s$ calculates the accuracy of each client's predictions of $B_t$ using true label of the $B_t$:
\begin{equation}
  a_i^t=AccuracyCal(\mathbf{k_i^t}, B_t).
\end{equation}
Then the clients with a low accuracy value over predicting $B_t$ are identified as malicious Byzantine clients.
\par Step-5: \ul{\textit{Global Model Updating}} After identifying the malicious clients within all clients, $s$ aggregates the knowledge $\mathbf{\hat{k}^t}$ from all clients as
\begin{equation}
  \mathbf{\hat{k}^t}=\sum_{i=1}^{u}\frac{e_i}{\sum_{i=1}^{u}e_i}\mathbf{\hat{k}^t}_i.
\end{equation}
Then the aggregated knowledge $\mathbf{\hat{k}^t}$ is used to derive the labels by the central server $s$
\begin{equation}
  \mathbf{\hat{y}^t}= argmax(\mathbf{\hat{k}^t}).
\end{equation}

\subsection{Bayesian Inference-based Reputation Mechanism}
The server $s$ keeps track of the reputation of all the clients $C$ in the model in a reputation list. Let $X_i$ be the $c_i$ client's reputation, which represents $s$'s opinion of how probable client $c_i$ is to be a Byzantine client. The accuracy $a_i^t$ of client $c_i$ from the first iteration to the $t$th iteration is used to compute $X_i$. When client $c_i$ sends a new update to server $s$, $s$ uses the accuracy $a_i^t$ to update the value of $X_i$.
\par At first, the reputation is neutral. With a probability of 50\%, server $s$ considers each client $c_i$ to be a benign client. The reputation of the server $s$ is updated when a new update $\mathbf{k_i^t}$ arrives at the central server. When the client $c_i$'s reputation falls below the threshold $r$, $s$ considers the client $c_i$ to be a Byzantine client and discards the client's update. When the $X_i$ surpasses the threshold $r$, the client $c_i$ updates are reviewed in the aggregation.
\par We employ Bayesian inference to construct our reputation mechanism. Each data prediction made by client $c_i$ faces two situations: wrong predictions or correct predictions. Thus, the use of binomial parameter distributions becomes a natural choice for our reputation mechanism. Let $Y_i$ be the event that the number of wrong predictions and correct predictions made by client $c_i$ is $\alpha_i$ and $\beta_i$. Given $X_i=\gamma_i$, the conditional probability is 
\begin{equation}
  Pr(Y_i|X_i=\gamma _i)=\left ( \frac{\alpha _i+\beta _i}{\alpha _i} \right )\gamma {_{i}}^{\alpha_i}\left ( 1-\gamma_{i} \right )^{\beta_{i}}\label{equation_1}
\end{equation}
where $\alpha_i$ and $\beta_i$ is the available evidence for the estimation of the $X$, and $\gamma_i$ is unknown. Eq. \ref{equation_1} indicates the likelihood function for $X$. According to Bayesian inference we compute the posterior probability as
\begin{equation}
  Pr(X_i=\gamma _i|Y_i)=\frac{Pr\left ( Y_{i}|X_{i}=\gamma_{i} \right )Pr(X_{i}=\gamma_{i})}{\int_{0}^{1}Pr\left ( Y_{i}|X_{i}=x \right )Pr(X_{i}=x)dx}\label{equation_2}.
\end{equation}
Given the posterior probability function, the final value for the expectation value of reputation $X$ is computed as
\begin{equation}
  E(X)=\int_{0}^{1}\frac{Pr\left ( Y_{i}|X_{i}=\gamma_{i} \right )Pr(X_{i}=\gamma_{i})}{\int_{0}^{1}Pr\left ( Y_{i}|X_{i}=x \right )Pr(X_{i}=x)dx}\gamma_{i}d\gamma_{i}\label{equation_3}.
\end{equation}
Furthermore, we decide to use the binomial parameter beta distribution to describe the distribution of X. Assume X is a random variable of the beta distribution with the parameters $(\alpha, \beta)$, the density function is
\begin{equation}
  f(x,\alpha,\beta)=\frac{1}{B(\alpha,\beta)}x^{\alpha-1}(1-x)^{\beta-1}\label{equation-4}
\end{equation}
where $B(\alpha, \beta)$ function is the beta function. Therefore we compute the expectation of $X$ as
\begin{equation}
  E(X)=\frac{\alpha}{\alpha+\beta}.
\end{equation}

Thus, the central server ${s}$ computes the reputation $X_i$ of each client ${c_{i}}$ as ${E(x_{i})=\frac{\alpha_{i}}{\alpha_{i}+\beta_{i}}}$. We set the reputation's initial value to 50\% by setting the initial value of $\alpha$ and $\beta$ to 1. This means that the chances for each client $c_ i$ of being a benign or malicious Byzantine client are the same. When a new iteration of EFL is completed, new evidence for the computation of the reputation is presented in the form of ${\alpha_{i}}'$ and ${\alpha_{i}}'$. The reputation is then computed by
\begin{equation}
  {E(x_{i})}'=\frac{(\alpha_{i}+{\alpha_{i}}')}{(\alpha_{i}+{\alpha_{i}}')+(\beta_{i}+{\beta_{i}}')}.
\end{equation}

\par In our conference version, we designed an aggregation rule which utilizes a threshold to identify the Byzantine clients. While in this work, we propose a new Byzantine-tolerant aggregation rule, FLPhish-weight.
\par\textit{\ul{FLPhish-weight}} Unlike the aggregation rule designed in our conference version, FLPhish-weight does not discard the potential Byzantine clients' updates. On the contrary, it enables the Byzantine clients to participate the aggregation using its reputation value as the aggregation weight. Due to our reputation mechanism, the Byzantine clients are offered a low reputation, so it has a lower influence on the aggregation process.
Give a reputation list $R=\left | x_{1},x_{1},x_{1},\cdots ,x_{n-1},x_{n} \right |$, the prediction results is 
\begin{equation}
  \mathbf{k_i^t}=\begin{vmatrix}
    p_{1,1} & p_{1,2} & \cdots  & p_{1,g-1} & p_{1,g}\\ 
    \vdots  & \vdots & \ddots  & \vdots & \vdots\\ 
    p_{n,1} & p_{n,2} & \cdots  & p_{n,g-1} & p_{n,g}
    \end{vmatrix}.
\end{equation}
Meanwhile, FLPhish-weight computes the aggregated knowledge, which is
  \begin{equation}
  \mathbf{\hat{k}^t}=\sum_{i=1}^{u}\frac{e_i}{\sum_{i=1}^{u}e_i}\mathbf{\hat{k}^t}_i\times x_{i}.
\end{equation}
Then the server $s$ uses the aggregated knowledge $\mathbf{\hat{k}^t}$ to get the labels
\begin{equation}
  \mathbf{\hat{y}^t}\gets argmax(\mathbf{\hat{k}^t}).
\end{equation} 
In a word, FLPhish-weight does not identify the Byzantine clients but treats the clients with a low reputation as `bad' clients and gives them lower weights.

@@

\section{Performance Evaluation}
In this section, we experimentally evaluate our FLPhish (noted as FLPhish(weight) in the following parts) against Byzantine attacks (denial-of-service attacks) under different experiment settings. Furthermore, we compare FLPhish(weight)'s performance with FedAvg \cite{ref_01_GoogleFL}, Median \cite{ref_13_defense}, and Trimmed Mean \cite{ref_13_defense}'s performance, and the evaluation results demonstrate that FLPhish(weight) outperforms these schemes in defending against Byzantine attacks. Furthermore, we compare our proposed aggregation rule, FLPhish(weight) with former aggregation rule used in our previous work \cite{li2021flphish}. Our previous work (noted as FLPhish($\tau$) in the following parts) utilized a threshold to identify the Byzantine clients. Here we set the threshold to 0.1 (noted as FLPhish($\tau=0.1$)), 0.2 (noted as FLPhish($\tau=0.2$)) and 0.5 (noted as FLPhish($\tau=0.5$)).

>>>>

\begin{abstract}
  Emerging as a promising distributed learning paradigm, federated learning (FL) has been widely adopted in many fields. Nonetheless, a big challenge for FL in real-world implementation is Byzantine attacks, where compromised clients can mislead or poison the training model by falsifying or manipulating the local model parameters. To solve this problem, in this paper, we present a reputation-based Byzantine robust-FL scheme (called FLPhish) for defending Byzantine attacks under the Ensemble Federated Learning architecture (called EFL). Specifically, we first develop a novel ensemble FL architecture, EFL, which allows FL compatible with different deep learning models in different clients. Second, we craft a phishing algorithm for the EFL architecture to identify possible Byzantine behaviors. Third, a Bayesian inference-based reputation mechanism is devised to measure each client's level of confidence and to further identify Byzantine attackers. Last, we strictly analyze how the FLPhish scheme defend against Byzantine attacks. Extensive experiments under different settings demonstrate that the proposed FLPhish achieves great efficacy in defending Byzantine attacks in EFL. FLPhish is tested with different fractions of Byzantine attackers and different degrees of distribution imbalance.
\end{abstract}

@@

\par Former researchers have offered certain Byzantine-robust techniques to deal with malicious Byzantine attackers under the FL application settings \cite{ref_12_defense,ref_13_defense,ref_15_defense,ref_16_defense,ref_17_defense,ref_28_defense,ref_29_defense,ref_30_defense,ref_31_defense,ref_32_defense}. Byzantine-robust techniques try to construct a global model with high accuracy in the presence of a finite number of malicious clients. According to their different mechanisms, we divide Byzantine-robust approaches into two major types. The first (named Byzantine-Detection) is based on the development of a Byzantine-robust aggregation algorithm that distinguishes suspected clients from benign clients. The suspected clients' gradient updates are subsequently removed from the aggregation process by the server. For instance, in the DRACO scheme proposed by Chen \textit{et al.}, each node analyzes duplicate gradients that the parameter server uses to mitigate the effects of adversarial updates \cite{ref_13_defense}. Another Byzantine-robust technique (named Byzantine-Tolerance) seeks to ensure that the aggregation process is tolerant to poisoned updates from Byzantine attackers without excluding Byzantine attackers. For example, in Median \cite{ref_16_defense}, the FL server sorts the values of each parameter and picks the median value of each parameter as the value to be utilized in global model updates. In this study, we provide a unique reputation-based phishing method (named FLPhish) to protect against Byzantine attacks in EFL. Our contributions are three-fold:
\begin{itemize}
  \item We design a new FL architecture, Ensemble Federated Learning (called EFL), which utilizes an unlabeled dataset to replace the gradient updates in typical FL. This architecture is more compatible with different deep learning models on different clients.
  \item We craft a `phishing' method based on EFL to detect Byzantine attacks. The `phishing' method employs an labeled dataset to detect the potential Byzantine attackers in the EFL architecture, which preserves the security of the EFL.
  \item We present a Bayesian inference-based reputation mechanism to promote FLPhish's aggregation. The reputation mechanism gives each client a reputation to measure its confidence value and identifies the clients with low reputation values as Byzantine attackers, which helps FLPhish identify the Byzantine attackers with higher accuracy.
\end{itemize}

\section{Related Work}
In this section, we discuss about the related research work about the proposed Byzantine defense methods in FL and the proposed reputation mechanism in cybersecurity research.
\subsection{Byzantine Defense Methods in Federated Learning}
Byzantine-robust schemes are very important for FL to enhance its security as Byzantine attacks can cause great damages to the FL system. Recent years have witnessed the increasing interest in the research of Byzantine-robust schemes in the context of FL. Most of the current Byzantine-robust FL methods tend to make a more robust aggregation rule which aims to tolerate the presence of Byzantine attackers. 
For example, in 2017, Chen \textit{et al.} developed an approach called Krum, which selects one client's update as a global model based on a square-distance score in each iteration \cite{ref_12_defense}.
In the same year, Blanchard \textit{et al}. proposed two Byzantine-tolerant FL aggregation rules called Trimmed mean and Median \cite{ref_16_defense}. Trimmed Mean considers each parameter of the model update individually. Trimmed Mean sorts the parameter of the model updates collected, and cuts off the largest ones and the smallest ones. Median sorts the values of each parameter of all local model updates as well. Besides it considers the median value of each parameter as the value of the parameter in the global model update. 
In 2018, Chen \textit{et al.} designed an approach called DRACO to evaluate redundant gradients that are used by the parameter server to eliminate the effects of adversarial updates. 
In 2019, Xie \textit{et al.} proposed Zeno, which uses a ranking-based preference mechanism \cite{ref_15_defense}. The server computes a score for each client by using the stochastic zero-order oracle. Then Zeno presents a ranking list of clients based on the estimated descent of the loss function and the magnitudes. At last, Zeno computes the global model update by aggregating the clients with the highest scores. 
In 2020, SLSGD developed by Xie \textit{et al.} also uses trimmed mean as the robust aggregation rules for Byzantine-robust FL \cite{ref_14_defense}. 
In the same year, Cao \textit{et al.} proposed a Byzantine-tolerant scheme: FLTrust to introduce the use of trust \cite{ref_17_defense}. In each iteration, the server calculates a trust score for each client at first and lowers the trust score if the client's local model update's direction deviates more from the direction of the global model update. The client with a trust score lower than the threshold is considered a malicious client.
In 2021, a privacy-enhanced FL (PEFL) framework is presented by Liu \textit{et al.}  \cite{ref_45_defense}. PEFL takes advantage of homomorphic encryption to protect the privacy of the clients. Furthermore, a channel using the effective gradient data extraction is provided for the server to punish poisoners.

@@

\par \textit{1) Denial-of-Service Byzantine Attack:} In denial-of-service attacks, the Byzantine attackers intend to disturb the global model, thus making it produce wrong predictions of the normal dataset \cite{ref_04_model,ref_06_model,ref_07_data,yang2017generative,sun2018data}. The label flipping attack in the current system model can be used by a malicious Byzantine attacker $b_i$ to launch Byzantine attacks against the global model. Label flipping attacks require $b_i$ to change the labels of training data while ensuring that the data's features remain unchanged \cite{ref_18_label_flipping}. The local model of the Byzantine attacker, $b_i$ is trained with incorrect labels, resulting in a `poisoned' model with low accuracy. Then Byzantine attacker $b_{i}$ dispatches the false model gradient updates to the central server. Therefore, the false model gradient updates cause the central server to learn the false knowledge from clients. The server $s$'s aggregation process is performed on FedAvg, which takes each client $c_{i}$'s dataset $d_{i}$'s size as the aggregation weight for $c_{i}$. This means that a client $c_{i}$ with a larger size of $d_{i}$ gets a larger aggregation weight. Meanwhile, FedAvg takes the size of $d_{i}$ declared by $c_{i}$ as $d_{i}$'s real size, which means $b_{i}$ can declare a fake size value larger than $d_{i}$'s real size value to increase the impact of the attack. If the weight of the malicious clients reaches a threshold, the central server is misguided to produce false predictions. 

@@

\par \textit{1)} The typical FL design has several flaws, including incompatibility with various deep learning models in different clients and significant communication costs. As a result, we created EFL, a novel FL architecture inspired by the idea of ensemble learning. It lowers the cost of communication overhead and expands our ability to defend against Byzantine attacks in FL.
\par \textit{2)} The proposed EFL architecture currently needs a robust Byzantine attack protection mechanism. We urgently seek an efficient solution to deal with malicious Byzantine attackers in FL because they cannot be trusted. In our proposed EFL architecture, we describe a phishing-based approach to guard against Byzantine attacks.
\par \textit{3)} As the performance of each client remains not stable in each iteration, it is important for our scheme to accurately measure each client's level of confidence in the long term. Therefore, we further propose an effective Bayesian inference-based reputation scheme based on our phishing-based model to spot Byzantine attacks compromised by malicious users.

@@

\begin{algorithm}[t]
  \caption{Phishing Mechanism} 
  \hspace*{0.02in} {\bf Input:} 
  each FL client $c_i$, $i=1,2,3,...,u$ with its local dataset $d_i$, $i=1,2,3,...,u$; an FL central server $s$ with the unlabeled dataset $D$ and labeled dataset $B$ preserved by itself; the number of FL training iterations $T$; the size of the unlabeled batch $n$ used in each training iteration; the size of the labeled batch $m$ used in each training iteration.\\
  \hspace*{0.02in} {\bf Output:} 
  output result
  \begin{algorithmic}[1]
    \State $\mathbf{m_i}$ $\gets$ each client $c_i$ train a local model using its local dataset $d_i$.
    \For{\textit{t=1,2,3,..,,T}}
      \State $s$ selects $D_t$ (containing $n$ samples) from $D$ and $B_t$ (containing $m$ samples) from $B$.
      \For{\textit{i=1,2,3,...,u}}
        \State $s$ sends $D_t$ and $B_t$ to $c_i$.
        \State $c_i$ makes predictions $\mathbf{k_i^t}$ of the $D_t$ and $B_t$.
        \State $c_i$ sends $\mathbf{k_i^t}$ to $s$.
        \State $s$ calculates the accuracy $a_i^t$ of the predictions of $B_t$ made by $c_i$ in $t$th procedure.
        \If{$a_i^t > r_q$}
          \State $q_i = 1$.
          \For{\textit{j=i,i+1,i+2,...,u-1}}
            \State $(d,c,\mathbf{k^t},q,a^t)_j \gets (d,c,\mathbf{k^t},q,a^t)_{j-1}$.
          \EndFor
        \EndIf
      \EndFor
      \State $\mathbf{K_t}$ = $KnowledgeEnsemble(\mathbf{k_1^t},\mathbf{k_2^t},\mathbf{k_3^t},...,\mathbf{k_u^t})$.
      \State $\mathbf{M}$ = $ModelUpdate(\mathbf{K_t}, D_t, \mathbf{M})$.
    \EndFor
    \State\Return $\mathbf{M}$
  \end{algorithmic}
  \end{algorithm}
Unlike benign clients, the malicious clients return the incorrect prediction to the central server $s$ to disturb the aggregation process.
\par Step-4: \ul{\textit{Byzantine Identifying}} After accepting the predictions $\mathbf{k_i^t}$ from each client $c_i$, $s$ needs to identify the Byzantine attackers among all the clients. The predictions of the \textit{`bait'} (the labeled dataset $B_t$) are extracted apart from $D_t$ from $\mathbf{k_i^t}$. Next, $s$ calculates the accuracy of each client's predictions of $B_t$ using true label of the $B_t$:
\begin{equation}
  a_i^t=AccuracyCal(\mathbf{k_i^t}, B_t).
\end{equation}
Then the clients with a low accuracy value over predicting $B_t$ are identified as malicious Byzantine attackers.
\par Step-5: \ul{\textit{Global Model Updating}} After identifying the malicious clients within all clients, $s$ aggregates the knowledge $\mathbf{\hat{k}^t}$ from all clients as
\begin{equation}
  \mathbf{\hat{k}^t}=\sum_{i=1}^{u}\frac{e_i}{\sum_{i=1}^{u}e_i}\mathbf{\hat{k}^t}_i.
\end{equation}
Then the aggregated knowledge $\mathbf{\hat{k}^t}$ is used to derive the labels by the central server $s$
\begin{equation}
  \mathbf{\hat{y}^t}= argmax(\mathbf{\hat{k}^t}).
\end{equation}

\subsection{Bayesian Inference-based Reputation Mechanism}
The server $s$ keeps track of the reputation of all the clients $C$ in the model in a reputation list. Let $X_i$ be the $c_i$ client's reputation, which represents $s$'s opinion of how probable client $c_i$ is to be a Byzantine attacker. The accuracy $a_i^t$ of client $c_i$ from the first iteration to the $t$th iteration is used to compute $X_i$. When client $c_i$ sends a new update to server $s$, $s$ uses the accuracy $a_i^t$ to update the value of $X_i$.
\par At first, the reputation is neutral. With a probability of 50\%, server $s$ considers each client $c_i$ to be a benign client. The reputation of the server $s$ is updated when a new update $\mathbf{k_i^t}$ arrives at the central server. When the client $c_i$'s reputation falls below the threshold $r$, $s$ considers the client $c_i$ to be a Byzantine attacker and discards the client's update. When the $X_i$ surpasses the threshold $r$, the client $c_i$ updates are reviewed in the aggregation.
\par We employ Bayesian inference to construct our reputation mechanism. Each data prediction made by client $c_i$ faces two situations: wrong predictions or correct predictions. Thus, the use of binomial parameter distributions becomes a natural choice for our reputation mechanism. Let $Y_i$ be the event that the number of wrong predictions and correct predictions made by client $c_i$ is $\alpha_i$ and $\beta_i$. Given $X_i=\gamma_i$, the conditional probability is 
\begin{equation}
  Pr(Y_i|X_i=\gamma _i)=\left ( \frac{\alpha _i+\beta _i}{\alpha _i} \right )\gamma {_{i}}^{\alpha_i}\left ( 1-\gamma_{i} \right )^{\beta_{i}}\label{equation_1}
\end{equation}
where $\alpha_i$ and $\beta_i$ is the available evidence for the estimation of the $X$, and $\gamma_i$ is unknown. Eq. \ref{equation_1} indicates the likelihood function for $X$. According to Bayesian inference we compute the posterior probability as
\begin{equation}
  Pr(X_i=\gamma _i|Y_i)=\frac{Pr\left ( Y_{i}|X_{i}=\gamma_{i} \right )Pr(X_{i}=\gamma_{i})}{\int_{0}^{1}Pr\left ( Y_{i}|X_{i}=x \right )Pr(X_{i}=x)dx}\label{equation_2}.
\end{equation}
Given the posterior probability function, the final value for the expectation value of reputation $X$ is computed as
\begin{equation}
  E(X)=\int_{0}^{1}\frac{Pr\left ( Y_{i}|X_{i}=\gamma_{i} \right )Pr(X_{i}=\gamma_{i})}{\int_{0}^{1}Pr\left ( Y_{i}|X_{i}=x \right )Pr(X_{i}=x)dx}\gamma_{i}d\gamma_{i}\label{equation_3}.
\end{equation}
Furthermore, we decide to use the binomial parameter beta distribution to describe the distribution of X. Assume X is a random variable of the beta distribution with the parameters $(\alpha, \beta)$, the density function is
\begin{equation}
  f(x,\alpha,\beta)=\frac{1}{B(\alpha,\beta)}x^{\alpha-1}(1-x)^{\beta-1}\label{equation-4}
\end{equation}
where $B(\alpha, \beta)$ function is the beta function. Therefore we compute the expectation of $X$ as
\begin{equation}
  E(X)=\frac{\alpha}{\alpha+\beta}.
\end{equation}

Thus, the central server ${s}$ computes the reputation $X_i$ of each client ${c_{i}}$ as ${E(x_{i})=\frac{\alpha_{i}}{\alpha_{i}+\beta_{i}}}$. We set the reputation's initial value to 50\% by setting the initial value of $\alpha$ and $\beta$ to 1. This means that the chances for each client $c_ i$ of being a benign or malicious Byzantine attacker are the same. When a new iteration of EFL is completed, new evidence for the computation of the reputation is presented in the form of ${\alpha_{i}}'$ and ${\alpha_{i}}'$. The reputation is then computed by
\begin{equation}
  {E(x_{i})}'=\frac{(\alpha_{i}+{\alpha_{i}}')}{(\alpha_{i}+{\alpha_{i}}')+(\beta_{i}+{\beta_{i}}')}.
\end{equation}

\par In our conference version, we designed an aggregation rule which utilizes a threshold to identify the Byzantine attackers. While in this work, we propose a new Byzantine-tolerant aggregation rule, FLPhish-weight.
\par\textit{\ul{FLPhish-weight}} Unlike the aggregation rule designed in our conference version, FLPhish-weight does not discard the potential Byzantine attackers' updates. On the contrary, it enables the Byzantine attackers to participate the aggregation using its reputation value as the aggregation weight. Due to our reputation mechanism, the Byzantine attackers are offered a low reputation, so it has a lower influence on the aggregation process.
Give a reputation list $R=\left | x_{1},x_{1},x_{1},\cdots ,x_{n-1},x_{n} \right |$, the prediction results is 
\begin{equation}
  \mathbf{k_i^t}=\begin{vmatrix}
    p_{1,1} & p_{1,2} & \cdots  & p_{1,g-1} & p_{1,g}\\ 
    \vdots  & \vdots & \ddots  & \vdots & \vdots\\ 
    p_{n,1} & p_{n,2} & \cdots  & p_{n,g-1} & p_{n,g}
    \end{vmatrix}.
\end{equation}
Meanwhile, FLPhish-weight computes the aggregated knowledge, which is
  \begin{equation}
  \mathbf{\hat{k}^t}=\sum_{i=1}^{u}\frac{e_i}{\sum_{i=1}^{u}e_i}\mathbf{\hat{k}^t}_i\times x_{i}.
\end{equation}
Then the server $s$ uses the aggregated knowledge $\mathbf{\hat{k}^t}$ to get the labels
\begin{equation}
  \mathbf{\hat{y}^t}\gets argmax(\mathbf{\hat{k}^t}).
\end{equation} 
In a word, FLPhish-weight does not identify the Byzantine attackers but treats the clients with a low reputation as `bad' clients and gives them lower weights.

@@

\section{Performance Evaluation}
In this section, we experimentally evaluate our FLPhish (noted as FLPhish(weight) in the following parts) against Byzantine attacks (denial-of-service attacks) under different experiment settings. Furthermore, we compare FLPhish(weight)'s performance with FedAvg \cite{ref_01_GoogleFL}, Median \cite{ref_13_defense}, and Trimmed Mean \cite{ref_13_defense}'s performance, and the evaluation results demonstrate that FLPhish(weight) outperforms these schemes in defending against Byzantine attacks. Furthermore, we compare our proposed aggregation rule, FLPhish(weight) with former aggregation rule used in our previous work \cite{li2021flphish}. Our previous work (noted as FLPhish($\tau$) in the following parts) utilized a threshold to identify the Byzantine attackers. Here we set the threshold to 0.1 (noted as FLPhish($\tau=0.1$)), 0.2 (noted as FLPhish($\tau=0.2$)) and 0.5 (noted as FLPhish($\tau=0.5$)).
